PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-03 paper/sec-results.tex
Typos
I think that I've included MArco's comments to Sect.3

In this section we demonstrate the capabilities of \textsc{PineAPPL} by
computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections are expected 
to be sizeable. In order to consider some realistic kinematics for these
processes, we resort to measurements commonly devised for inclusion in PDF
fits. Our aim is twofold. First, we want to validate the results
obtained with \textsc{PineAPPL}; second, we want to assess the
impact of the EW corrections for usual experimental setups. We describe, first,
the processes and measurements that we consider, then the computational
settings that we adopt, and finally the results that we obtain.

@@

\paragraph{Drell--Yan lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
mass energy of 7~TeV in the high-mass region
($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
We also select the distributions, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
7~TeV~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. The latter is not included in the NLO
QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
corrections occur only at NNLO, and are therefore not considered here.
EW corrections for this process were computed in
Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW), mainly from $q\bar{q}$
scattering, see Appendix~\ref{app:lumis} for details.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
at NLO, $\mathcal{O}(\alpha_s^3)$. They make up the NLO QCD
computation. The NLO QCD+EW computation includes the LO contribution
$\mathcal{O}(\alpha_s\alpha)$ and the NLO contributions
$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ and the
corresponding higher-order EW correction. EW corrections for this process
were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion,
see Appendix~\ref{app:lumis} for details.

\paragraph{$Z$-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
included in any PDF determination. Because it has sub-percent uncertainties,
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of 8~TeV, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alpha_s\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alpha_s^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed correction, $\mathcal{O}(\alpha_s\alpha^3)$. EW corrections for
this process were computed in
Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 100 (165) parton luminosities, mainly
from $qg$ and $\bar{q}g$ scattering, see Appendix~\ref{app:lumis} for details.

@@

\paragraph{Top-quark pair production.}

>>>>

In this section we demonstrate the capabilities of \textsc{PineAPPL} by
computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections may have a
sizeable effect on the accuracy of the theoretical predictions.
In order to consider some realistic kinematics for these
processes, we resort to measurements commonly devised for inclusion in PDF
fits. Our aim is twofold. First, we want to validate the results
obtained with \textsc{PineAPPL}; second, we want to assess the
impact of the EW corrections for usual experimental setups. We describe, first,
the processes and measurements that we consider, then the computational
settings that we adopt, and finally the results that we obtain.

@@

\paragraph{Drell--Yan lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
mass energy of 7~TeV in the high-mass region
($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
We also select the distributions, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
7~TeV~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
Sect.~\ref{sec:pineappl-example}, should PI contributions be taken into account,
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alpha_s\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. The latter is not included in the NLO
QCD computation, but it is in the NLO QCD+EW computation. Mixed QCD-EW
corrections occur only at NNLO, and are therefore not considered here.
EW corrections for this process were computed in
Refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
see Appendix~\ref{app:lumis} for details.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
at NLO, $\mathcal{O}(\alpha_s^3)$. They make up the NLO QCD
computation. The NLO QCD+EW computation includes the LO contribution
$\mathcal{O}(\alpha_s\alpha)$ and the NLO contributions
$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ and the
corresponding higher-order EW correction. EW corrections for this process
were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
6 (36) parton luminositites at NLO QCD (NLO QCD+EW), 
see Appendix~\ref{app:lumis} for details.

\paragraph{$Z$-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
energy of 13~TeV~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
included in any PDF determination. Because it has sub-percent uncertainties,
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of 8~TeV, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alpha_s\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alpha_s^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed correction, $\mathcal{O}(\alpha_s\alpha^3)$. EW corrections for
this process were computed in
Refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 100 (165) parton luminosities,
see Appendix~\ref{app:lumis} for details.

@@

\paragraph{Top-quark pair production.} We now consider
